%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     File: ExtendedAbstract_concl.tex                               %
%     Tex Master: ExtendedAbstract.tex                               %
%                                                                    %
%     Author: Andre Calado Marta                                     %
%     Last modified : 27 Dez 2011                                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main conclusions of the study presented in short form.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:concl}

The nonlinear control law for fast dynamics was submitted to different types of perturbations and inversion errors. The controller showed to be robust to not only to errors in inertia estimation as well as small system failures. For more serious control perturbations however, the aircraft could not, as would be expected, follow the desired inputs. Using a $99.5\%$ smaller inertia relative to its true value in the NLI algorithm, increasing by $200\%$ the drag coefficient or by heavily reducing the ability of the control surfaces to influence the plane's dynamics, the aircraft's behaviour showed much higher reference tracking errors, sometimes even becoming uncontrollable. Concluding this first section the designed controller, using a model based approach, proved to be robust to most external perturbations and internal errors. 

Taking firstly the errors caused by errors in parameter estimations and gain tuning (for the linear law controlling the aircraft's model linearised by the FBL), the network showed improvements in robustness and reduced errors in airspeed and heading following, when compared to the same controller without the network. Similar tests were made with reduced control from actuators and in icing conditions. For the actuator failure case although the network slightly improve heading convergence times, reducing $C_{\delta_{ail}}, C_{\delta_{ele}}, C_{\delta_{rud}}$ by 80\% is still a too big perturbation for a commercial aircraft to recover from. For icing condition were simulated reduced lift coefficient, increased drag and reduced roll control ($C_{\delta_{ail}}$ was reduced by 30\%). For this case however, while the non corrected was unable to follow a heading and flight path angle references, this was not the case once the online neural network was added to the system. Indeed the network allowed the aircraft to follow a sinusoidal heading reference and to reduce the difference between $\gamma$ and its desired value. 

The same network architecture was used for all cases described above. Taking this into account it can be concluded that the goal of designing a neural network that would make the original NLI law more robust and able to adapt to different perturbations was indeed achieved.